---
title: "Lab 1"
author: "anonymous"
date: "9/5/2024"
output: pdf_document
---

# CSC110: Data Science & Society Lab 1

Welcome to CSC 110 Lab 1! In this lab, you will visualize data on economic mobility in the U.S. from [Opportunity Insights] (<https://opportunityinsights.org/>) using the ggplot2 package.

## INSTRUCTIONS

-   Do not include your names in this file or in the name of the file
-   Run the chunk of code that creates the chetty_top100 data frame (below)
-   Write R code in the each code chunk that creates the plots described, and record short answers below the code chunk in a paragraph or bullet points
-   Knit your code regularly (to html is quickest and easiest) to be sure you don't lose vital pieces of code along the way
-   Knit your final code to a pdf file, and submit your pdf file in Gradescope. Your Rmd file will stay stored in JupyterHub if we need to refer back to it.

## Set up code

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
```

## Filter the data

Read and filter data to get data only for the 100 largest CZs. You will work with chetty_top100 throughout this lab.

```{r, include=FALSE}
chetty <- read_excel("Lab1_Chetty_2014.xlsx", skip=1)

# filter for top 100 commuting zones
chetty_top100 <- chetty %>%
  filter(top_100==1)

# remove the larger data set with all commuting zones from the work space
rm(chetty)
```

# Part I: Economic Mobility & Household Income Across Commuting Zones

In Part I you will explore the relationship between economic mobility and a CZ characteristic not mentioned in the Executive Summary: household income per capita (hhi_percap). The mobility measure that you will use in this analysis captures the probability that a child born to a parent in quintile 1 moves to income quintile 5 as an adult (prob_q1q5).

1.  

    1.  Make a scatterplot with household income per capita on the x-axis, and mobility on the y-axis.
    2.  Describe the chart: what is the range of the x-axis? What is the range of the y-axis? Do you think there is a relationship between these two variables?

    ```{r}

    ```

2.  

    1.  Use color to represent the geographic region (region) to your scatterplot.
    2.  What patterns does this reveal? Describe the distribution of the data, by region.
    3.  Which region(s) appears to have the most CZs with mobility\>10%?
    4.  Which region(s) appears to have the most CZs with mobility\<5%?\

    ```{r}

    ```

3.  

    1.  Represent geographic region on your scatterplot using shape instead of color.
    2.  Compare the use of color vs shape to represent the region: what are the benefits and drawbacks of each?\

    ```{r}

    ```

4.  

    1.  Going back to the chart you made in 2.1, which uses color to represent the region, add another aesthetic to represent the size of the population (pop_2000, population from the 2000 Census ).
    2.  Describe any relationships between size and region.

    ```{r}

    ```

5.  

    1.  Split your plot into facets to display scatterplots of your data by census region.
    2.  Compare this split plot to the combined plot from #3. Are there aspects of the relationship between hhi_percap and mobility that are easier to detect in the faceted plot than in the combined plot?
    3.  Which regions appear to have a relatively stronger relationship between hhi_percap and mobility?\

    ```{r}

    ```

6.  

    1.  Add information on the census division to your chart using the color aesthetic.
    2.  What does this reveal about divisional differences in the West?

    ```{r}

    ```

7.  

    1.  Create a plot of the relationship between hhi_percap and mobility with two layers: (1) A scatterplot colored by region, and (2) a smooth fit chart with no standard error also colored by region.
    2.  What patterns does this illustrate in the data?\

    ```{r}

    ```

8.  

    1.  Create a bar chart that displays the count of CZs by census region and fill each bar using information on census division.
    2.  What do you learn from this chart?
    3.  Make new bar charts with position "dodge" and "fill"
    4.  What is the relative advantage of each of the three bar charts?

    ```{r}

    ```

# Part II: Answering your own research question

Use the Chetty data to answer a different research question by choosing a CZ characteristic you have not yet explored (i.e., other than hhi_percap, social_capital and gini). Recreate the plots in #1 through #7 above, and optionally add additional charts if there are other questions you want to explore. *Be sure to summarize and interpret your findings below each plot.*
