---
title: "Tidycensus"
author: ""
date: "2024-10-24"
output: html_document
---

## Review

Go to the Davidson Community Research Fellows (CRF) Community Dashboard here: <https://crf-dashboard.rc.davidson.edu/>

Look at the bar graph under the Housing tab.

## Setup

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

# If you have not already installed the tidycensus package, copy and paste this line below into your console and run it once.
# install.packages("tidycensus")

library(tidyverse)
library(tidycensus)

# Set your API key (from homework)
census_api_key("insertYourAPIKeyHere", install = TRUE, overwrite = TRUE)
readRenviron("~/.Renviron")

```

## Part 1

Use your census API key along with the tidycensus function `load_variables()` to get our variables.

`load_variables()` executes a call to one of the census API endpoints. It accepts two parameters:(1) census year and (2) dataset ("acs5"). It returns all available variables for that subset.

Use this knowledge to retrieve only the relevant variables for renters based on Tuesday's class.

```{r}
# Set the census year we want to query
v_year <- 2020

# Create the rent_vars data frame using load_variables()


# Overwrite the rent_vars data frame with just a list of the variables we need


# Load the list of variables into a vector


```

------------------------------------------------------------------------

## Part 2

Now that we know what variables to use, let's retrieve the actual ACS data using the `get_acs()` function:

`get_acs()` executes a call to another census API endpoint. It accepts several required parameters, including a list of variables. It returns the census data you will need to recreate the CRF bar chart.

Make a new data frame named "acs_data" that contains all the variables and numbers to be plotted in the bar graph, and pipe it into a ggplot to make the bar graph. Compare your result to the dashboard. What are the differences?

```{r}
# Invoke get_acs() to retrieve the data we need


# Use geom_col() to plot the data in a column chart


```

---

## Part 3

Resolve the differences between your chart and the CRF chart using:
- factors
- `scale_fill_manual()` (using our_palette)
- `scale_y_continuous()` (using housing_max)
- `coord_flip()`
- `labs()`

What parts of your code would change if you were making the graph for homeowners?

```{r}
# Set our color palette
our_palette <- c("#F8766D", "#00A9FF", "#00BE67", "#CD9600", "#7CAE00", "#00BFC4", "#C77CFF", "#FF61CC")

# Use factors to change the sorting of our X and Y axis labels
c(
  "Less than $10,000",
  "$10,000 to $19,999",
  "$20,000 to $34,999",
  "$35,000 to $49,999",
  "$50,000 to $74,999",
  "$75,000 to $99,999",
  "$100,000 or more"
)

c(
  "Less than 20.0 percent",
  "20.0 to 24.9 percent",
  "25.0 to 29.9 percent",
  "30.0 to 34.9 percent",
  "35.0 to 39.9 percent",
  "40.0 to 49.9 percent",
  "50.0 percent or more"
)

# Throw the data into ggplot!


```
