---
title: "Lab 3, CSC 110, Fall 2024"
author: "anonymous"
date: ''
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Background

In this lab, you will work with data from the Quality of Life Explorer created by the UNCC Urban Institute in collaboration with the city of Charlotte, Mecklenburg County, and nearby townships. The data file *qol_lab3.xls* is provided for you. This dataset describes how various aspects of Charlotte residents' "quality of life" varies according to neighborhood. You can explore and [learn more about this project here] <http://charlottenc.gov/HNS/CE/CommunityInfo/Pages/QOL.aspx>.

# Instructions

-   It might help to knit this document before you start your work to make the instructions and questions easier to read.
-   Leave the author as anonymous.
-   Make your plots look polished by including axis labels, making appropriate choices for binwidths, etc.
-   Review the geoms presented in [R4DS Chapter 10.5 (Covariation)](https://r4ds.hadley.nz/eda#covariation). Each coding question in Part I should have **at minimum** one visualization that uses a geom from 10.5.
-   Turn in the knitted pdf file in Gradescope and make sure to enter the page number(s) where each answer can be found.

\newpage

# Preparing for the lab

## Question 1

(a) In Excel or Numbers, open the data file for this lab. Examine the data and the "metadata" sheets. What does each observation in the data represent? Will you be able to answer questions about individual towns, zip codes or census blocks in Mecklenburg County? Why or why not?

|                          |
|--------------------------|
| Answer for (a) goes here |

(b) How many different variables are in the dataset? Approximately how many different variables are described in the metadata sheet? Across how many different social issues?

|                          |
|--------------------------|
| Answer for (b) goes here |

(c) Explain the significance of the highlighted rows in the metadata worksheet, relative to the data worksheet.

|                          |
|--------------------------|
| Answer for (c) goes here |

\newpage

# Part I. Median household income and adolescent birth rate

The LOTF report indicates that, while unintended pregnancies occur across the income distribution, low income women are five times more likely to have an unintended pregnancy than wealthier women. The task force cites research suggesting that having a child before one is ready can have negative outcomes for the life trajectory of young parents and their children. The first section of this lab asks you to explore how adolescent birth rate and income are related at the neighborhood level in Mecklenburg county.

## Question 1

Visualize the covariation between the rate of adolescent births and median household income. What do you observe about the relationship between these variables?

```{r echo=TRUE}
#Question 1

```

|                                  |
|----------------------------------|
| Written answer for (1) goes here |

\newpage

## Question 2

Create a boxplot of the rate of adolescent birth by household income quartile. Use the features of the boxplot (i.e, the bar, box, whiskers and dots) to interpret your findings and discuss the pros and cons of this visualization in 2-4 sentences, including breaking income up by quartile.

```{r echo=TRUE}
#Question 2

```

|                                  |
|----------------------------------|
| Written answer for (2) goes here |

\newpage

## Question 3

Use the cut_width strategy for "binning" the household income variable. Discuss the pros and cons of this visualization in 2-4 sentences.

```{r echo=TRUE}
#Question 3

```

|                                  |
|----------------------------------|
| Written answer for (3) goes here |

\newpage

## Question 4

(a) Create a visualization that compares the distributions of the rate of adolescent birth for low-income neighborhoods (with a median HHI below the poverty line for a family of 4 in Charlotte, as given in the LOTF report), and high-income neighborhoods (with a median HHI at or above 200% of the poverty line).

```{r echo=TRUE}
#Question 4(a)

```

\newpage

(b) Create a numerical summary that shows the adolescent birth rates for these two groups.

```{r echo=TRUE}
#Question 4(b)

```

(c) Is this comparison a good test of the LOTF report claim that the "teen pregnancy rate is five times higher for women living in poverty"? Why or why not?

|                                   |
|-----------------------------------|
| Written answer for 4(c) goes here |

\newpage

## Question 5

(a) Visualize the combined distribution of adolescent births, household income, and access to adequate prenatal care. Note that you may want to bin one or more of these variables to visualize these relationships, and you will need to find a way to represent a third variable.

```{r echo=TRUE}
#Question 5(a)

```

\newpage

(b) In 2-4 sentences, describe why you decided to assign variables to the aesthetics you chose. How did these choices help you tell a compelling story with this visualization?

|                                   |
|-----------------------------------|
| Written answer for 5(b) goes here |

\newpage

## Question 6

The LOTF report states, "when women and their partners in our community do decide to become pregnant, prenatal and postnatal care are critically important to providing a healthy start for a child." Given this goal, what implications might your findings in Question 5 have for LOTF recommendations regarding income, adolescent pregnancy and prenatal care? Keep your answer between 1-2 paragraphs.

|                                |
|--------------------------------|
| Written answer for 6 goes here |

\newpage

# Part II. Conducting your own Exploratory Data Analysis

In the second half of the lab, you will use the QOL data to conduct your own exploratory data analysis (EDA) inspired by an open question in the LOTF report. Your EDA will be graded on your choice of an appropriate research question, the clarity of your visualizations, and how well your visualizations allow you to recognize patterns in your data and provide insight into the question you have posed. This is similar to what you will need to do for your final project.

In this section, you should pose and answer at minimum four iterative, related EDA questions, using a minimum of 3 different variables (as in Questions 2 through 5 in Part I). Write as though you are guiding future students through an exploration of the data, along with an answer key where you provide your code and written analysis. Your reader should be able to follow how your research progresses as you pose your overarching question, then prep and visualize the data, draw your first conclusion based on your work, and then use that to narrow or adjust your focus as you progress to the next question, and the one that follows, and so forth.

Number each question individually using R markdown Heading 2 and include each research question directly below its heading (an example is visible on the next page), then follow that with your code chunks, visualizations, and written analysis of your findings. Be sure to clearly state your EDA question, explain why you chose the visualizations that you did, and describe your findings in 1-2 well-written paragraphs. You will be graded on the quality and clarity of your writing here!

When inserting your R chunks, remember to use `echo=TRUE` so we can see your code and its output in the final product. You may also use `\newpage` to add page breaks between the different parts of your analysis.

For guidance on drafting a research question, [read R4DS 10.1 thru 10.2](https://r4ds.hadley.nz/eda#introduction).

\newpage

## Main research question

LOTF claims that access to education and career readiness services improve economic stability. Is there data to prove that educational success yields economic success? What other factors may be influencing measures such as employment? This part of the lab will investigate the relationship between education and employment, with consideration of other factors that may impact this relationship.

## Research question #1

Type your question here

```{r echo=TRUE}


```

Summarize your findings:

|     |
|-----|
|     |

\newpage

## Research question #2

Type your question here

```{r echo=TRUE}

```

Summarize your findings:

|     |
|-----|
|     |

: \newpage

## Research question #3

Type your question here

```{r echo=TRUE}

```

Summarize your findings:

|     |
|-----|
|     |

: \newpage

## Research question #4

Type your question here

```{r echo=TRUE}

```

Summarize your findings:

|     |
|-----|
|     |

: \newpage

## Honor Code Pledge

On my honor I have neither given nor received unauthorized information regarding this work, I have followed and will continue to observe all regulations regarding it, and I am unaware of any violation of the Honor Code by others.

(Type the word "pledged" below to pledge this assignment for all lab team members.

|     |
|-----|
|     |
