---
title: "Class 11: Tibbles, Tribbles, and Tidy Data - Oh my!"
author: "Pete Benbow"
date: "Oct 1, 2024"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("tidyverse")
library(tidyverse)
```

## A tibble called south

```{r}
# Build a tibble called "south"
(south <- tibble(
  state = c("NC", "SC", "GA", "TN"),
  pct_black = c(.2, .3, .4, .25),
  pct_hisp = c(.1, .2, .2, .15),
  pct_asian = c(.1, .2, .1, .1),
  pct_white = c(.6, .3, .3, .5)
))

# Note the grain of the data!
```

Thought question: Is this a tidy tibble? What kind of plot might you want to make with these data? Could you do it without first modifying the data frame?

## Tidying tibbles

Tidy your south tibble. [Read the documentation](https://tidyr.tidyverse.org/reference/pivot_longer.html) and try to find three different ways to select the variables to pivot:

```{r}
# 1

# 2

# 3

```

## Tidying column names

Now let's clean up column names. See if you can find two different ways to remove "pct\_" from the resulting variable values. [Read the documentation](<https://tidyr.tidyverse.org/reference/pivot_longer.html>) to find some alternatives.

```{r}
# 1 

# 2

```

## Plotting the output after pivoting or unpivoting:

```{r}
# Make a bar graph showing demographic breakdown by state

  
```

## Tidy us_rent_income

```{r}
# Preview the US rent data and note the grain
us_rent_income

# Pivot the data using pivot_wider() to get one row per US state
# HINT: you may need to use the c() function for one of the pivot arguments

```

## Tidy relig_income

Find three different ways to employ pivot_longer() to tidy this data

```{r}
# Preview the relig_income data and note the grain
relig_income

# 1

# 2

# 3

```

## Introducing tribble()

```{r}
# Construct south again, using tibble()
(south <- tibble(
  state = c("NC", "SC", "GA", "TN"),
  pct_black = c(.2, .3, .4, .25),
  pct_hisp = c(.1, .2, .2, .15),
  pct_asian = c(.1, .2, .1, .1),
  pct_white = c(.6, .3, .3, .5)
  )
)

# Construct south again, using tribble()


# What differences do you notice between tibble() and tribble()? The output is the same, but do you see advantages to one method versus the other?
  
```