---
title: "Synthesizing activity"
author: "Pete Benbow"
date: "2024-10-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

```

## Review

Go to the Davidson Community Research Fellows (CRF) Community Dashboard here: <https://crf-dashboard.rc.davidson.edu/>

Look at the bar graph under the Housing tab.

-   What can you conclude about affordable housing in Mecklenburg County?
-   What variables would you need to include in a hypothetical data frame to recreate this bar graph?

## Some new functions to think about using:

-   `n_distinct()`
-   `str_detect()`

## Setup

Read data frames from the census2019 and ACS_variables_2019 rds files.

```{r}
census2019 <- readRDS("census2019.rds")
ACS <- readRDS("ACS_variables_2019.rds")

```

## Part 1

Write code to answer each of the following about census2019:

1.  How many distinct census tracts are represented? Can you find three different ways to answer this question using dplyr?

2.  Make a list of the distinct ACS variables in census2019. How many distinct variables are there in this dataset?

3.  How many ACS variables are recorded for each census tract?

```{r}
#a How many census tracts are represented?

```

```{r}
#b Make a list of the unique ACS variables in census2019  

```

```{r}
#c How many ACS variables are recorded for each census tract?

```

## Part 2

Answer each of the following about the ACS data frame:

1.  How many rows are in this tibble? What does each row represent?

2.  How many distinct ACS variables contain "PERCENTAGE OF HOUSEHOLD INCOME" in their concept?

3.  How many distinct ACS concepts contain "PERCENTAGE OF HOUSEHOLD INCOME" in their name?

4.  Which of these might be relevant for making the bar chart under the Housing tab in the CRF dashboard? 

```{r}
#2.1 How many rows are in the ACS data frame?

```

```{r}
#2.2 How many distinct ACS variables contain "PERCENTAGE OF HOUSEHOLD INCOME" in their concept?

```

```{r}
#2.3 How many distinct ACS concepts contain "PERCENTAGE OF HOUSEHOLD INCOME" in their name?

```

```{r}
#2.4 Which of these might be relevant for making the bar chart under the Housing tab in the CRF dashboard? 

```
