---
title: 'Class 7: Histograms and case_when'
author: "Pete Benbow"
date: "Sep 17, 2024"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
```

```{r warning = FALSE}
# Now we get real with Chetty, starting with the downloaded file

typ = append(c("numeric", "text", "text"), rep(c("numeric"),38))

chetty <- read_excel("Chetty_Intergenerational Mobility_tables.xls", sheet="Online Data Table 8", skip=6, col_types=typ) %>%
  filter(CZ>0)

# Note that mobility measures are in a different sheet!
```


## Making summary tables with count()

1. Use the count function to display the number of urban and non-urban CZs
```{r}
# Hint: use glimpse in the console to print out new, non-standard variable names

```

## Histograms of continuous variable(s)

2. Explore the variation in `School Expenditure per Student` with histograms. What is a good number of bins, or binwidth? Is there any surprising structure to these data? Are there any outliers? What are the non-finite values?  
```{r}
#2a Experimenting with bins


#2b Experimenting with binwidth

```

3. On your own or with a partner, repeat #2 with `Teacher Student Ratio` and `High School Dropout Rate (Income Adjusted)`
```{r}
#3a Teacher Student Ratio


#3b High School Dropout Rate (Income Adjusted)


```


4. Use mutate() and case_when() to make a new categorical variable with 3 or 4 different values for the level of school expenditures. Note that this would allow you to use different colors or facets in a scatter plot or bar graph for the level of school expenditure (try it if you have time!)
```{r}

```


