---
title: 'Class 14 Activity: Filtering Joins'
author: "Pete Benbow"
date: "Oct 15, 2024"
output:
  html_document:
    df_print: paged
---

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(nycflights13)
```

## Revisiting mutating joins: Part 1

```{r echo=TRUE}
# Slim down the flights dataset
flights2 <- flights %>% 
  select(year, time_hour, origin, dest, tailnum, carrier)

# Inspect the new flights data frame


# Inspect the Airlines data frame


# Note the column they have in common. This will be used as our join key by default! (natural join - not explicit)

# Now use a simple left join to combine these two data frames, and look at the results.
flights2 %>%

# Inspect the weather data frame and note the data it provides us, and at what grain


# left join to the weather DF and select a few columns: origin, time_hour, temp, and wind_speed:
flights2 %>%

```

## Revisiting mutating joins: Part 2

```{r echo=-TRUE}
# Now let's join some more data
# Inspect the planes data frame and note the grain of the data


# Use left join to determine how many engines and seats were on each flight in our flights dataset
flights2 %>%

# Note the fact that some of our flights are missing data! We have a lot of NA values being returned.


```

## Specifying join keys
In our previous example, we noted that some of our flights are missing data

```{r echo=TRUE}
# What happens if we do a left join from our flights data frame to the entire planes data frame?
flights2 %>%
  

# Now let's specify the join key explicitly:
flights2 %>%


# Another way to use the join_by argument is to specify join keys when the same type of data may be contained in two different columns.
# For example: origin airports versus destination airports. They both contain airport codes!
# But the relevant column in our airports data frame is named "faa", so a natural (implicit) join is impossible here.
# So we need to specify the join keys explicitly:
flights2 %>%


# Now use TWO join functions to bring in airport names for both destinations AND origins
flights2 %>%
  

# Now use INNER_join to return only the rows that have a destination in our airports table
flights2 %>%
  

```

## Filtering joins
There are two types of filtering joins: semi-joins and anti-joins.
NOTE: Unlike mutating joins, filtering joins do not return any columns from the right-hand table. Their best use is as a way to identify the rows in one table that either do (semi-join) or do NOT (anti-join) have a match in the other table.

### Semi-joins
Semi-joins keep all rows in x that have a match in y.

```{r echo=TRUE}
# use a semi-join to filter the airports data frame to show just the origin airports
airports %>% 

# This returns a list of all records in the airports data frame that are contained in the origin column of our flights data frame.
# This also reinforces something we already knew: that our nycflights13 dataset indeed contains only data about flights originating from airports in the New York metropolitan area.

# In contrast, if we use a semi-join to filter based on destination, we'll get a list of all airports that are listed as destinations in our flights data frame.
airports %>% 

```

### Anti-joins
Anti-joins return all rows in x that do NOT have a match in y. This is very useful for trying to identify missing values in a dataset.

```{r echo=TRUE}
# Find flight destinations that are missing from airports by looking for flights that do not have a matching destination in our airport data frame
flights2 %>% 



# Which tailnums appear in our flights data frame that do NOT appear in our planes data frame?
flights2 %>%

```

