---
title: "R4DS notes - Chapter 3 - Data Transformation"
author: "Pete Benbow"
date: "Sep 3, 2024"
output: word_document
---

This document is meant to act as a sample for how a student can take notes and complete materials in the R4DS textbook. This example comes from [Chapter 3 of R4DS](https://r4ds.hadley.nz/data-transform#introduction).

# 3.1 Intro

## Install and load packages

```{r}
install.packages("nycflights13")
library(nycflights13)
library(tidyverse)
```

## Explore the data in a tibble

You can use `View(flights)` to view the data interactively in RStudio. Otherwise, this technique is a good way to get a quick glimpse of the first few rows in a dataset.

Note the locations of the data types below each variable, such as dbl, int, and chr.

```{r}
flights
```

## dplyr Basics

dplyr is included with tidyverse and is used for data manipulation. The first argument is always a dataframe, while the subsequent arguments usually describe what variables to operate on. The final output is always a new frame.

The "pipe" operator is a great way to pass output between functions.

```{r}
flights |> 
  filter(dest == "CLT") |>
  group_by(year, month, day) |>
  summarize(
    arr_delay = mean(arr_delay, na.rom = TRUE)
  )

```

# 3.2 Rows

## filter()

```{r}
#1 flights with departure delay greater than 120 minutes
flights |>
  filter(dep_delay > 120)

#2 flights that department on December 31
flights |>
  filter(month == 12 & day == 31)

#3 flights that departed in January or February
flights |>
  filter(month == 1 | month == 2)

#4 flights that departed in January or February, different technique using %in% and c() to concatenate
flights |>
  filter(month %in% c(1,2))

```

You can also assign the result of your query to a new data frame using the \<- assignment operator, like so:

```{r}
# Create the data frame
dec31 <- flights |>
  filter(month == 12 & day == 31)

# View the "dec31" tibble
dec31

```

## arrange()

arrange() changes the order of the rows based on the value of the columns. It is akin to an ORDER BY statement in SQL.

```{r}
#1 arrange flights by year, month, day, and departure time in ascending order (default)
flights |>
  arrange(year, month, day, dep_time)

#2 arrange flights in order from most delayed to least delayed
flights |>
  arrange(desc(dep_delay))

```

## distinct()

distinct() finds all unique rows in a dataset, and can be used in many ways. For instance, it can be used to remove duplicate values, but it can also be used to find all distinct airport codes.

The `.keep_all` option can be used to keep other columns when filtering for unique rows.

```{r}
#1 Remove duplicate rows, if any
flights |> 
  distinct()

#2 Find all unique origin airports
flights |>
  distinct(origin)

#3 Use keep-all
flights |>
  distinct(origin, dest, .keep_all = TRUE)

```

# 3.3 Columns

## mutate()

mutate() allows us to add new columns calculated from existing columns.

You can also use arguments like `.before` and `.after` and `.keep` to modify your results.

```{r}
#1 compute the gain (how much a delayed flight made up in the air) and speed in miles PER HOUR
flights |>
  mutate(
    gain = dep_delay - arr_delay,
    speed = distance / air_time * 60
  )

#2 use the .before argument to reposition the variables
flights |>
  mutate(
    gain = dep_delay - arr_delay,
    speed = distance / air_time * 60,
    .before = 1
  )

#3 use the after argument to reposition the variables
flights |>
  mutate(
    gain = dep_delay - arr_delay,
    speed = distance / air_time * 60,
    .after = 4
  )

#4 use the keep argument to reposition the variables, and use the "used" argument to keep only the columns in our mutation
flights |>
  mutate(
    gain = dep_delay - arr_delay,
    speed = distance / air_time * 60,
    .keep = "used"
  )

```

## select()

select() can be used to only return the variables we want. It functions much the same as the SELECT clause in SQL.

```{r}
#1 select columns by name -- note how this differs from distinct()
flights |> 
  select(year, month, day)

#2 select all columns between two columns using the : operator
flights |> 
  select(year:day)

#3 select all EXCEPT those between two columns using the ! operator
flights |> 
  select(!year:day)

#4 select all columns where the data type is character
flights |> 
  select(where(is.character))

#5 rename a variable on the fly with select()
flights |> 
  select(tail_num = tailnum)

```

## rename()

If you want to keep all existing variables and just rename a few:

```{r}
flights |>
  rename(tail_num = tailnum)

```

## relocate()

Use relocate() to move variables around

```{r}
#1 Move some variables to the front
flights |>
  relocate(time_hour, air_time)

#2 Use the .after argument to relocate a series of columns after another column
flights |>
  relocate(year:dep_time, .after = time_hour)

#3 Use the .before argument to relocate all columns starting with "arr" to before the dep_time column
flights |>
  relocate(starts_with("arr"), .before = dep_time)

```

# 3.4 Pipes

You can combine pipes with these mutations to run your data through a series of transformations

```{r}
flights |>
  # get all flights to Charlotte
  filter(dest == "CLT") |>
  # calculate speed
  mutate(speed = distance / air_time * 60) |>
  # select only the columns we need
  select(year:day, dep_time, origin, dest, carrier, flight, speed) |>
  # sort the result by speed in descending order
  arrange(desc(speed))

```
