---
title: 'CSC 110: Quiz 2'
author: "Anonymous"
date: "Oct 1, 2024"
output:
  word_document: default
  html_document:
    df_print: paged
---

## Instructions

-   You must work alone on this quiz. You may ask me a clarifying question by DM, but you may not get help from anyone.
-   You may use all resources from the class, including the textbook, readings, videos, in-class activities and notes
-   You may also look for help on functions inside of R Studio
-   **Collaboration with other students is not allowed**
-   Put answers to your written (non-code) questions in the boxes provided below each code chunk.
-   Knit your code to pdf (or to Word and then print to pdf) and upload your pdf to Moodle.
-   Be sure to *LABEL* all your axes and legends

The data for this quiz are the same that we used for the Class 8 in-class activity.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(readxl)

```

## Read in the data

```{r echo=TRUE}
nc <- read_excel("NC_ECE_2007-2014.xls")
```

Questions begin on next page

\newpage

1.  
    a.  Make a new data frame called nc14 that contains all NC facilities in the year 2014, with the variables fname, zip, ftype, p_pov, med_income, QRIS_ERS, and a new variable p_cap = enroll/capacity. You will use this data frame in the remaining questions.

```{r echo=TRUE}
#1(a) Create new data frame


```

\newpage

2.  

    a.  Make a new data frame that shows the number of facilities evaluated in each zip code in 2014, and the value of p_pov for each zipcode. Sort by the number of facilities in decreasing order. **Be sure this new data frame shows in the output.**

    b.  Make a plot from the data frame you made in part (a) that demonstrates variation in percent poverty across zip codes in NC

    c.  In 2-3 sentences, explain why your plot in (b) is different from a plot that demonstrates variation in p_pov in the original nc14 data frame

```{r echo=TRUE}
#2(a). Create new data frame


#2(b). Make a plot


```

+-------------------------+
| Written answer to 2(c): |
+-------------------------+

\newpage

3.  

    a.  Add a new variable to nc14 that lumps together various facility types into five groups, based on the value of ftype, as follows:
        -   Independent
        -   Franchise
        -   Religious sponsored
        -   Federal, Head Start or Local public school
        -   All others Show the data with this new column.
    b.  Make a plot to show the variation in p_cap across these five groups.
    c.  In 2-3 sentences, describe the plot you just created and what it indicates about your p_cap variable across these different groups.

```{r echo=TRUE}
#3(a). Add a new variable 


#3(b). Make a plot


```

+-------------------------+
| Written answer to 3(c): |
+-------------------------+

\newpage

4.  
    a.  Make a boxplot to visualize covariation between QRIS_ERS and med_income, binning med_income to treat it as a categorical variable, and representing the number of observations in each category by the width of the corresponding box.
    b.  In 2-3 sentences, describe the visualization you just created and what it communicates about possible covariation between these two variables.

```{r echo=TRUE}
#4 Boxplot


```

+-------------------------+
| Written answer to 4(b): |
+-------------------------+

\newpage

5.  

    a.  Visualize the relationship between med_income and QRIS_ERS using a scatter plot.
    b.  Visualize the same relationship using geom_bin2d.
    c.  In 2-3 sentences, discuss the pros and cons of each of these visualizations.

```{r echo=TRUE}
#5(a). Visualize


#5(b). Visualize some more


```

+-------------------------+
| Written answer to 5(c): |
+-------------------------+

\newpage

## Honor Code Pledge

On my honor I have neither given nor received unauthorized information regarding this work, I have followed and will continue to observe all regulations regarding it, and I am unaware of any violation of the Honor Code by others.

+-----------------------------------------------------------+
| Type your full name in this box to pledge the assignment: |
+-----------------------------------------------------------+
